Response to Reviewer One

### 2021-05-07 Scripts/Reviews/reviewer_one.Rmd
Responses to reviewer one

- *Response:* In the section "High present-day climate risk of on transboundary fisheries management" we describe early shifts in the shared distribution of transboundary stocks including the cases of Humboldt squid (*Dosidicus gigas*) and Atlantic mackerel (*Scomber scombrus*) both in the early 2000s. We have included some more punctual examples of documented shifts between 2006 and 2021. It reads on line **xx** of page **XX**: "Similar shifts have been documented for multiple European stocks [@Baudron:2020dj] like European hake (*Merluccius merluccius*) [@Baudron:2015il] as well as...

>>>>

- **Response:** In the section "High present-day climate risk of on transboundary fisheries management" we describe early shifts in the shared distribution of transboundary stocks including the cases of Humboldt squid (*Dosidicus gigas*) and Atlantic mackerel (*Scomber scombrus*) both in the early 2000s and have included a couple more punctual examples of documented shifts between 2006 and 2021. However, there is not a vast documentation on shifts in the distribution of transboundary species (i.e., specifically from one EEZ to another). Mapping these shifts is out of the scope of the current project as there is an ongoing effort to document the global hifts of transboundary species.
